---
title: "naive-approach"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(joint)
```


## Create synthetic data

Create joint distribution

```{r}
set.seed(123)
n <- 100000

# more complex sim for later

gender <- tibble(values = c("female", "male", "other"), probability = c(0.49, 0.49, 0.2))
# ns_sec <- tibble(values = c("1-2", "3", "4", "5", "6-7", "8", "9 - other", "9 - students"), probability = c(0.5, 0.1, 0.06, 0.06, 0.09, 0.02, 0.03, 0.03))
ns_sec <- tibble(values = c("0", "1", "2", "3", "4", "5", "6", "7"), probability = c(0.5, 0.1, 0.06, 0.06, 0.09, 0.02, 0.03, 0.03))
msoa <- tibble(values = letters[1:5], probability = 0.2)

sim <- tibble(.rows = n) |>
  rowwise() |>
  mutate(age = runif(n=1, min = 18, max = 95) |> floor(),
         gender = sample(gender$values, prob=gender$probability, 1, replace = TRUE),
         ns_sec = sample(ns_sec$values, prob=ns_sec$probability, 1, replace = TRUE),
         msoa = sample(msoa$values, prob=msoa$probability, 1, replace = TRUE)) |>
  ungroup()



# Calculate joint distribution
joint <- sim |>
  group_by(gender, ns_sec, msoa) |>
  summarize(count = n()) |>
  ungroup() |>
  mutate(proportion = count / sum(count))
```

Create marginal distributions

```{r}
marginal_gender <- joint |>
  group_by(gender) |>
  summarize(marginal_count = sum(count)
            # marginal_proportion = sum(proportion)
            )

marginal_ns_sec <- joint |>
  group_by(ns_sec) |>
  summarize(marginal_count = sum(count)
            # marginal_proportion = sum(proportion)
            )

marginal_msoa <- joint |>
  group_by(msoa) |>
  summarize(marginal_count = sum(count)
            # marginal_proportion = sum(proportion)
            )
```


## Set up the form of the joint distribution that we desire

Empty joint. This is what we want to fill correctly with the numbers of people in each row.


```{r}
empty_joint <- tidyr::crossing(gender = gender$values,
                               ns_sec = ns_sec$values,
                               msoa = msoa$values)
```

Add unique id to each row

```{r}
empty_joint <- empty_joint |>
  rowid_to_column()
```


## Iterative proportional fitting

```{r}
library(ipfr)
```


```{r}
targets <- list()
targets$gender <- marginal_gender |>
  pivot_wider(names_from = gender, values_from = marginal_count)
targets$ns_sec <- marginal_ns_sec |>
  pivot_wider(names_from = ns_sec, values_from = marginal_count)
targets$msoa <- marginal_msoa |>
  pivot_wider(names_from = msoa, values_from = marginal_count)

result <- ipu(empty_joint, targets,
              relative_gap = 0.00001,
              max_iterations = 10000,
              absolute_diff = 0.01,
              )
weights <- result$weight_tbl
answer <- joint |> left_join(weights)

answer |> ggplot(aes(count, weight)) + geom_point() + geom_abline(slope = 1)
```

```{r}
answer <- answer |> 
  mutate(difference = weight - count)
answer |>
  ggplot(aes(count, 100*difference/count)) + geom_point() + geom_abline(slope = 0)
```


## Issues

The main issues is that we were forced to use target distributions that are just vectors. In general we want to use n-dimensional target distributions.
